Prediction model for PMI using ROSMAP Reprocessed RNASeq

### 2016-09-02 code/Rmd/PredictPMI.Rmd
Minor changes

---
title: "Prediction model for PMI using ROSMAP Reprocessed RNASeq"
author: "Thanneer Perumal"
date: "`r date()`"
output: html_document
---

```{r knit2synapse, eval=FALSE}
library(knitr)
library(knit2synapse)
library(synapseClient)

>>>>

---
title: "Prediction model for PMI using ROSMAP Reprocessed RNASeq"
author: "Thanneer Perumal"
date: "`r date()`"
output: html_document
---
```{r knit2synapse, eval=FALSE}
library(knitr)
library(knit2synapse)
library(synapseClient)
